---
title: "Blog Post 4"
author: "GWXYZ"
date: '2022-11-03'
slug: []
categories: []
tags: []
description: data cleaning and deeper exploration of data
toc: yes
authors: []
series: []
lastmod: '2022-11-03T21:18:45-04:00'
featuredVideo: ~
featuredImage: ~
---
## Change of dataset
  NBA player stats 
https://github.com/peasant98/TheNBACSV/blob/master/nbaNew.csv

This dataset contains massive NBA player stats from 1950-2017. It contains all performance information of each NBA player in 67 NBA seasons. There are 24625 rows and 54 columns. The data was originally collected from the website Basketball Reference. We intend to analyze the data and predict the future salary and value of each player and predict sports decisions . We also want to find the trend of the development of basketball. One challenge for us is to understand the relationship between each terminology in the basketball field.

## Data cleaning
```{r}

library(readr)
library(tidyverse)
nba <- read_csv("/Users/xuduoyifu/Desktop/大四/MA415/HW/ma4615-fa22-final-project-gwxyz/dataset/nbaNew.csv", col_types = cols(PlayerSalary = col_number(), `TS%` = col_number(),`ORB%` = col_number(),`DRB%` = col_number(),`TRB%` = col_number(),`AST%` = col_number(),`STL%` = col_number(),`BLK%` = col_number(),`TOV%` = col_number(),`USG%` = col_number(),`FG%` = col_number(),`3P%` = col_number(),`2P%` = col_number(),`eFG%` = col_number(),`FT%` = col_number()))
nba_clean<- select(nba, -(blanl), -(blank2), -(`3P`), -(`3PA`),-(`3P%`))%>%
  na_if("")%>%
  filter(!row_number() %in% c(24625, 24626, 24627, 24628, 24628))
```
We clean the meaningless part of the dataset after row 24625 and change some colume type into number.

## Graph
```{r}
nba_clean %>%
  filter(Pos %in% c("PF","SF", "C", "SG", "PG"))%>%
  filter(`ORB%` >0, `ORB%`<25)%>%
  ggplot() +
  geom_bar(aes(x = ORB, fill = Pos)) 
```

```{r}
nba_clean %>%
  filter(Pos %in% c("PF","SF", "C", "SG", "PG"))%>%
  filter(`ORB%` >0, `ORB%`<25)%>%
  ggplot() + 
  stat_summary(aes(x = Pos, y = `ORB%`),
  fun = mean, geom = "bar")

```
We tried to find relations between different variables, and we get the following model after many attempts.

## Model
```{r}
LinearModel <- lm(PF ~ DRB, data=nba_clean)
beta <- coef(LinearModel)

nba_clean %>% 
  ggplot(aes(DRB,PF)) +
  geom_point()+
  geom_abline(intercept = beta[1],
              slope = beta[2], color = "red")

summary(LinearModel)
```
This model has a high significant value for every parameter and the adjusted R squared is good.